---
title: "Lidya's Website"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 
---

## About Me

Hi! My name is Lidya and I'm a **second-year Master's student in Epidemiology**. While I have had the opportunity to work on many projects in a variety of different areas, I would say my research interests are in **preventive health** and **health disparities**, with a special focus on **immigrant/minority populations.**

Over the length of this course, I'm excited to learn practical skills in R in applying statistical methods. I'm especially looking forward to learning more about data visualization techniques!
<br/>
<br/>

#### Education: 
*Johns Hopkins School of Public Health*, (2020-present)
<br/> 
MHS in Epidemiology | Certificates: Population and Health, Health Disparities and Health Inequality

*Johns Hopkins University*, (2016-2019)
<br/> 
BA in Public Health Studies

<br/>

#### Previous Work:

```{r library, echo=FALSE}
library(knitr)
Dates <- c("06/2021 - 08/2021", "09/2019 - 08/2020", "01/2017 - 07/2019", "06/2017 - 08/2017")
Location <- c("Acumen, LLC", "University of Bern", "Center for Global Tobacco Control", "MD Anderson Cancer Center")
Position <- c("Writer/Coordinator Intern", "Fulbright Scholar", "Research Assistant", "CPRIT/CURE Summer Intern")
Description <- c("Provide analytical support for research and consulting projects for Centers for Medicare and Medicaid", "Lead qualitative study on migrant women's experiences navigating the Swiss healthcare system", "Conduct research on targeted media campaigns for e-cigarette products", "Support genomic research on early detection of hepatocellular carcinoma")
previouswork <- data.frame(Dates, Location, Position, Description)
kable(previouswork)
```


---

## Fun Facts

Some fun facts about me are...<br/>
<br/>
🍝 My favorite food is pasta <br/><br/>
📚 I really enjoy learning languages — I am a native English and Amharic speaker and I am learning German, Italian, French, and ASL (although I'm at different levels with each!)<br/><br/>
🌱 I love growing indoor plants<br/><br/>
🎷 I know how to play the saxophone<br/><br/>
🦊 Red pandas are my favorite animal


---

## Radio Garden

Have you ever wanted to know what's on the radio on the other side of the world? [Radio Garden](http://radio.garden/) is a non-profit digital research project that lets you listen to over 8,000 radio stations across the globe!



Some of my personal favorites are: <br/>

  * [Rahel Radio](http://radio.garden/listen/rahel-radio/koxxTffV) in Addis Ababa, Ethiopia
  * [JP Bossa Nova](http://radio.garden/listen/jovem-pan-jp-bossa-nova/AMdrxhw6) in São Paulo, Brazil
  * [LagosJump Radio](http://radio.garden/listen/lagosjump-radio/bauREgSK) in Lagos, Nigeria
  * [J1 Radio Extra](http://radio.garden/listen/j1-radio-extra/xcMFulFT) in Tokyo, Japan

<br/><br/>